---
pagetitle: "campsistrans"
date: ""
author: ""
output: github_document
---

# pmxtran
A library dedicate to drug model conversion in pharmacometrics.

## Requirements

* Python framework and Pharmpy package must be installed beforehand
* R packages pmxmod must also be installed

## Installation
Install the current development version:
  
```{r, eval=FALSE}
devtools::install_github("Calvagone/campsistrans", ref="main", auth_token="AUTH_TOKEN", force=TRUE)
```

## Some examples

### Import NONMEM control stream

First import the `campsistrans` package:

```{r, message=FALSE}
library(campsistrans)
```

Let's have a quick look at the NONMEM control stream we're going to import:

```{r comment=''}
cat(readLines("data-raw/advan4_trans4"), sep = "\n")
```

Let's name our model parameters first by defining a mapping object.

```{r}
mapping <- mapping(
    theta = c(KA=1, CL=2, V2=3, V3=4, Q=5),
    omega = c(KA=1, CL=2, V2=3, V3=4, Q=5),
    sigma = c(PROP=1))
```

Let's then import this model using `campsistrans`.
By default, the initial values are used as reference values in the model.

```{r}
object <- importNONMEM("data-raw/advan4_trans4", mapping, estimate=FALSE)
```

Convert this object to a CAMPSIS model:

```{r}
model <- object %>% export(dest="campsis")
show(model)
```

Simulate it using CAMPSIS:

```{r}
library(campsis)
dataset <- Dataset(10)
dataset <- dataset %>% add(Bolus(time=0, amount=1000))
dataset <- dataset %>% add(Observations(times=seq(0,24, by=0.5)))

results <- simulate(model, dataset, dest="RxODE", seed=1)
spaghettiPlot(results, "CP")
```
